### 2021-04-12 paper/natastron/ArXiV/si.tex
Added ArXiV stuff
prepped the ArXiV submission

\documentclass[12pt]{article}
\setlength{\textwidth}{167mm}
\setlength{\headsep}{0mm}
\setlength{\headheight}{0mm}
\setlength{\textheight}{230mm}
\setlength{\oddsidemargin}{1.6mm}
\setlength{\evensidemargin}{1.6mm}
\setlength{\topmargin}{4.6mm}

\usepackage{chngcntr}
\usepackage{xspace}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{lscape}
\usepackage{longtable}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage[figurename={Supplementary Figure}, tablename={Supplementary Table}]{caption}
\usepackage{booktabs}
\usepackage[ ]{hyperref}
\graphicspath{{Images/}}
%\usepackage[symbol]{footmisc}

% Astronomical abbreviations (thanks to Dan Huber)
\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
\newcommand{\dnu}{\mbox{$\Delta \nu$}\xspace}
\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
\newcommand{\logg}{\mbox{$\log(g)$}\xspace}
\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
\newcommand{\msun}{\mbox{$\mathrm{M}_{\odot}$}\xspace}
\newcommand{\lsun}{\mbox{$\mathrm{L}_{\odot}$}\xspace}
\newcommand{\mearth}{\mbox{$\mathrm{M}_{\oplus}$}\xspace}
\newcommand{\rsun}{\mbox{$\mathrm{R}_{\odot}$}\xspace}
\newcommand{\kepler}{\emph{Kepler}\xspace}
\newcommand{\tess}{\emph{TESS}\xspace}
\newcommand{\ktwo}{K2\xspace}
\newcommand{\gaia}{\emph{Gaia}\xspace}

\begin{document}

@@

 \begin{figure*}
	\centering
	\includegraphics[width=.99\textwidth]{Images/modelfit.pdf}
	\caption{A power spectrum constructed from four years of \kepler observations of 16 Cyg A (KIC 12069424). Plotted over the top is the model resulting from the fit to the data described in this work. The model implements both the mode frequencies, seen on the right hand side of the plot, and the convective background, the effects of which are seen on the left. Low frequencies have been cropped out for clarity. \textit{Inset}: A zoom in on a radial (right) and quadrupole (left) ($\ell = 0, 2$) pair of modes. The quadrupole mode is split into five components by the star's rotation. Due to the star's inclination angle with respect to us, two out of five peaks are more distinct. The height and spacing of the mode components is a function of the star's rotational splitting ($0.56\, \mu\rm{Hz}$, equivalent to $P = 20.5\, \rm{days}$) and angle of inclination ($45^\circ$).}
	\label{fig:modelfit}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Images/priors.pdf}
	\caption{\textbf{Comparisons between posterior estimates of rotational parameters (data points and error bars) and the priors on these parameters (shaded regions).} The data are sorted from young stars (left) to old (right). Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$). Both the prior and values for $P$ are a transformation of the upper two parameters (see text). In all cases, the extent of the error bars and shaded regions indicate the 68\% credible interval of the posterior and prior distributions respectively. The solid lines indicate the median of the prior distributions. In this figure, results with means and errorbars that closely resemble the prior distribution can be interpreted as prior-dominated (i.e. poorly informed by the data). All stars are sorted and coloured and sorted by age. In the case of inclination angle $i$ and rotation period $P$, the displayed priors are transformed from the priors imposed on the sampled parameters from which their posteriors were derived.}
	\label{fig:priors}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{Images/litcomp_alt2.pdf}
	\caption{\textbf{Comparisons between posterior estimates of rotational parameters from this work and the literature}. Literature values are taken from LEGACY and `Kages' \cite[private communication]{davies+2016, lund+2017}. Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$). Fractional differences are plotted against stellar rotation obtained in this work. The $\Delta$ indicates the fractional difference between this work and the literature (i.e. stars above the zero-line have higher values in this work). The right hand panels the distribution of the fractional differences around the zero line. The colour legend is consistent throughout all panels. The x-axis units on the right hand panels are equivalent to the y-axis of the left hand panels. 10 stars have been omitted from this plot and are discussed in more detail in the text: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have extremely low rotation periods in Kages, with high uncertainties. Conversely, KICs 6603624, 8760414 and 8938364 have extremely high rotation periods in LEGACY with low uncertainties. Error bars represent the 68\% confidence intervals. In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
	\label{fig:legacykages}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\textwidth]{Images/seis_comparison_rot_alt2.pdf}
	\caption{\textbf{Fractional differences between posterior estimates of asteroseismic rotation period from this work.} Literature sources are: Davies et al. (2015) \cite{davies+2015} (16 Cyg A \& B), Nielsen et al. (2015) \cite{nielsen+2015} (5 stars) and Benomar et al. (2018) \cite{benomar+2018} (40 stars). We used the reported parameter $a_{1}$ from the latter, which represents the rotational splitting in the case of uniform latitudinal rotation in their model. The dashed line represents the median of the sample shown, with the dotted lines representing the $15.9^{\rm{th}}$ and $84.1^{\rm{st}}$ percentiles. Error bars represent the 68\% confidence intervals. In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
	\label{fig:literaturecomp}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{Images/vsini_comparison_new.pdf}
	\caption{\textbf{Comparisons between asteroseismic and spectroscopic measures of projected surface rotation, $\textrm{v}\sin(i)$.} All asteroseismic (x-axis) values are from this work, all spectroscopic (y-axis) values are from the literature. \textit{Left}: comparisons to 81 stars values reported in LEGACY and Kages. \textit{Right}: comparisons to 16 stars observed by Benomar et al. (2015) \cite{benomar+2015}. Asteroseismic values are transformed from projected splitting ($\nu_s\sin(i)$) using the asteroseismic radius measurements presented in LEGACY and `Kages'. Horizontal error bars represent the 68\% confidence intervals. Vertical error bars represent the formal uncertainty on the published spectroscopic values. The solid lines indicate the 1:1 line, while the dash-dotted lines represent the 2:1 and 1:2 lines. The dashed lines indicate the location of $\textrm{v}\sin(i) = 5\, \rm{kms^{-1}}$, the point at which surface and seismic measures of projected rotation begin to differ strongly \cite{tayar+2015}.}
	\label{fig:vsinilit}
\end{figure}

@@

\section{Supplementary Table}
\input{tabulate.tex}

\bibliographystyle{naturemag}
\bibliography{library.bib} % if your bibtex file is called example.bib

\end{document}

>>>>

\renewcommand{\figurename}{Supplementary Figure}

@@

 \begin{figure}
	\centering
	\includegraphics[width=.99\textwidth]{modelfit.pdf}
	\caption{A power spectrum constructed from four years of \kepler observations of 16 Cyg A (KIC 12069424). Plotted over the top is the model resulting from the fit to the data described in this work. The model implements both the mode frequencies, seen on the right hand side of the plot, and the convective background, the effects of which are seen on the left. Low frequencies have been cropped out for clarity. \textit{Inset}: A zoom in on a radial (right) and quadrupole (left) ($\ell = 0, 2$) pair of modes. The quadrupole mode is split into five components by the star's rotation. Due to the star's inclination angle with respect to us, two out of five peaks are more distinct. The height and spacing of the mode components is a function of the star's rotational splitting ($0.56\, \mu\rm{Hz}$, equivalent to $P = 20.5\, \rm{days}$) and angle of inclination ($45^\circ$).}
	\label{fig:modelfit}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{priors.pdf}
	\caption{\textbf{Comparisons between posterior estimates of rotational parameters (data points and error bars) and the priors on these parameters (shaded regions).} The data are sorted from young stars (left) to old (right). Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$). Both the prior and values for $P$ are a transformation of the upper two parameters (see text). In all cases, the extent of the error bars and shaded regions indicate the 68\% credible interval of the posterior and prior distributions respectively. The solid lines indicate the median of the prior distributions. In this figure, results with means and errorbars that closely resemble the prior distribution can be interpreted as prior-dominated (i.e. poorly informed by the data). All stars are sorted and coloured and sorted by age. In the case of inclination angle $i$ and rotation period $P$, the displayed priors are transformed from the priors imposed on the sampled parameters from which their posteriors were derived.}
	\label{fig:priors}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{litcomp_alt2.pdf}
	\caption{\textbf{Comparisons between posterior estimates of rotational parameters from this work and the literature}. Literature values are taken from LEGACY and `Kages' \cite[private communication]{davies+2016, lund+2017}. Shown are projected splitting ($\nu_{\rm s}\sin(i)$), inclination angle ($i$, sampled as $\cos(i)$) and rotation period ($P$). Fractional differences are plotted against stellar rotation obtained in this work. The $\Delta$ indicates the fractional difference between this work and the literature (i.e. stars above the zero-line have higher values in this work). The right hand panels the distribution of the fractional differences around the zero line. The colour legend is consistent throughout all panels. The x-axis units on the right hand panels are equivalent to the y-axis of the left hand panels. 10 stars have been omitted from this plot and are discussed in more detail in the text: KICs 5094751, 6196457, 8349582, 8494142, 8554498, 105114430 and 11133306 all have extremely low rotation periods in Kages, with high uncertainties. Conversely, KICs 6603624, 8760414 and 8938364 have extremely high rotation periods in LEGACY with low uncertainties. Error bars represent the 68\% confidence intervals. In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
	\label{fig:legacykages}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\textwidth]{seis_comparison_rot_alt2.pdf}
	\caption{\textbf{Fractional differences between posterior estimates of asteroseismic rotation period from this work.} Literature sources are: Davies et al. (2015) \cite{davies+2015} (16 Cyg A \& B), Nielsen et al. (2015) \cite{nielsen+2015} (5 stars) and Benomar et al. (2018) \cite{benomar+2018} (40 stars). We used the reported parameter $a_{1}$ from the latter, which represents the rotational splitting in the case of uniform latitudinal rotation in their model. The dashed line represents the median of the sample shown, with the dotted lines representing the $15.9^{\rm{th}}$ and $84.1^{\rm{st}}$ percentiles. Error bars represent the 68\% confidence intervals. In cases where stars had asymmetric error bars, the larger of the two was used when propagating uncertainty for the purposes of this figure.}
	\label{fig:literaturecomp}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{vsini_comparison_new.pdf}
	\caption{\textbf{Comparisons between asteroseismic and spectroscopic measures of projected surface rotation, $\textrm{v}\sin(i)$.} All asteroseismic (x-axis) values are from this work, all spectroscopic (y-axis) values are from the literature. \textit{Left}: comparisons to 81 stars values reported in LEGACY and Kages. \textit{Right}: comparisons to 16 stars observed by Benomar et al. (2015) \cite{benomar+2015}. Asteroseismic values are transformed from projected splitting ($\nu_s\sin(i)$) using the asteroseismic radius measurements presented in LEGACY and `Kages'. Horizontal error bars represent the 68\% confidence intervals. Vertical error bars represent the formal uncertainty on the published spectroscopic values. The solid lines indicate the 1:1 line, while the dash-dotted lines represent the 2:1 and 1:2 lines. The dashed lines indicate the location of $\textrm{v}\sin(i) = 5\, \rm{kms^{-1}}$, the point at which surface and seismic measures of projected rotation begin to differ strongly \cite{tayar+2015}.}
	\label{fig:vsinilit}
\end{figure}

@@

%\bibliographystyle{naturemag}
%\bibliography{library.bib} % if your bibtex file is called example.bib
\addcontentsline{toc}{section}{References}
\begin{thebibliography}{99}
	\makeatletter
	\addtocounter{\@listctr}{78}
	\makeatother
	\expandafter\ifx\csname url\endcsname\relax
	\def\url#1{\texttt{#1}}\fi
	\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
	\providecommand{\bibinfo}[2]{#2}
	\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{hogg2012}
\bibinfo{author}{Hogg, D.~W.}
\newblock \bibinfo{title}{Data analysis recipes: {{Probability}} calculus for
	inference}.
\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
\bibinfo{pages}{arXiv:1205.4446} (\bibinfo{year}{2012}).

\bibitem{davies+2014}
\bibinfo{author}{Davies, G.~R.}, \bibinfo{author}{Chaplin, W.~J.},
\bibinfo{author}{Elsworth, Y.} \& \bibinfo{author}{Hale, S.~J.}
\newblock \bibinfo{title}{{{BiSON}} data preparation: A correction for
	differential extinction and the weighted averaging of contemporaneous data}.
\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
\textbf{\bibinfo{volume}{441}}, \bibinfo{pages}{3009--3017}
(\bibinfo{year}{2014}).

\bibitem{appourchaux+2016}
\bibinfo{author}{Appourchaux, T.} \emph{et~al.}
\newblock \bibinfo{title}{Oscillation mode linewidths and heights of 23
	main-sequence stars observed by {{{\emph{Kepler}}}}
	{\emph{(}}{{{\emph{Corrigendum}}}}{\emph{)}}}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
\textbf{\bibinfo{volume}{595}}, \bibinfo{pages}{C2} (\bibinfo{year}{2016}).

\bibitem{rasmussen+williams2006}
\bibinfo{author}{Rasmussen, C.~E.} \& \bibinfo{author}{Williams, C. K.~I.}
\newblock \emph{\bibinfo{title}{Gaussian Processes for Machine Learning}}.
\newblock Adaptive Computation and Machine Learning (\bibinfo{publisher}{{MIT
		Press}}, \bibinfo{address}{{Cambridge, Mass}}, \bibinfo{year}{2006}).

\bibitem{toutain+appourchaux1994}
\bibinfo{author}{Toutain, T.} \& \bibinfo{author}{Appourchaux, T.}
\newblock \bibinfo{title}{Maximum likelihood estimators: {{An}} application to
	the estimation of the precision of helioseismic measurements}.
\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
\textbf{\bibinfo{volume}{289}}, \bibinfo{pages}{649--658}
(\bibinfo{year}{1994}).

\bibitem{gizon+solanki2003}
\bibinfo{author}{Gizon, L.} \& \bibinfo{author}{Solanki, S.~K.}
\newblock \bibinfo{title}{Determining the {{Inclination}} of the {{Rotation
			Axis}} of a {{Sun}}-like {{Star}}}.
\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
\textbf{\bibinfo{volume}{589}}, \bibinfo{pages}{1009} (\bibinfo{year}{2003}).

\bibitem{handberg+campante2011}
\bibinfo{author}{Handberg, R.} \& \bibinfo{author}{Campante, T.~L.}
\newblock \bibinfo{title}{Bayesian peak-bagging of solar-like oscillators using
	{{MCMC}}: A comprehensive guide}.
\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
\textbf{\bibinfo{volume}{527}}, \bibinfo{pages}{A56} (\bibinfo{year}{2011}).

\bibitem{appourchaux+1998}
\bibinfo{author}{Appourchaux, T.}, \bibinfo{author}{Gizon, L.} \&
\bibinfo{author}{{Rabello-Soares}, M.-C.}
\newblock \bibinfo{title}{The art of fitting p-mode spectra. {{I}}. {{Maximum}}
	likelihood estimation}.
\newblock \emph{\bibinfo{journal}{Astron. Astrophys. Supplement Series}}
\textbf{\bibinfo{volume}{132}}, \bibinfo{pages}{107--119}
(\bibinfo{year}{1998}).

\bibitem{anderson+1990}
\bibinfo{author}{{Anderson}, E.~R.}, \bibinfo{author}{{Duvall}, J., Thomas~L.}
\& \bibinfo{author}{{Jefferies}, S.~M.}
\newblock \bibinfo{title}{{Modeling of Solar Oscillation Power Spectra}}.
\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
\textbf{\bibinfo{volume}{364}}, \bibinfo{pages}{699} (\bibinfo{year}{1990}).

\bibitem{gelman2006}
\bibinfo{author}{Gelman, A.}
\newblock \bibinfo{title}{Prior distributions for variance parameters in
	hierarchical models (comment on article by {{Browne}} and {{Draper}})}.
\newblock \emph{\bibinfo{journal}{Bayesian Analysis}}
\textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{515--534}
(\bibinfo{year}{2006}).

\bibitem{ballot+2006}
\bibinfo{author}{Ballot, J.}, \bibinfo{author}{Garcia, R.~A.} \&
\bibinfo{author}{Lambert, P.}
\newblock \bibinfo{title}{Rotation speed and stellar axis inclination from p
	modes: How {{CoRoT}} would see other suns}.
\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
\textbf{\bibinfo{volume}{369}}, \bibinfo{pages}{1281--1286}
(\bibinfo{year}{2006}).

\bibitem{ballot+2008a}
\bibinfo{author}{Ballot, J.}, \bibinfo{author}{Appourchaux, T.},
\bibinfo{author}{Toutain, T.} \& \bibinfo{author}{Guittet, M.}
\newblock \bibinfo{title}{On deriving p-mode parameters for inclined solar-like
	stars}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
\textbf{\bibinfo{volume}{486}}, \bibinfo{pages}{867--875}
(\bibinfo{year}{2008}).
\newblock \eprint{0803.0885}.

\bibitem{kass+raftery1995}
\bibinfo{author}{Kass, R.~E.} \& \bibinfo{author}{Raftery, A.~E.}
\newblock \bibinfo{title}{Bayes {{Factors}}}.
\newblock \emph{\bibinfo{journal}{Journal of the American Statistical
		Association}} \textbf{\bibinfo{volume}{90}}, \bibinfo{pages}{773--795}
(\bibinfo{year}{1995}).

\bibitem{beck2000}
\bibinfo{author}{Beck, J.~G.}
\newblock \bibinfo{title}{A comparison of differential rotation measurements -
	({{Invited Review}})}.
\newblock \emph{\bibinfo{journal}{Solar Physics}}
\textbf{\bibinfo{volume}{191}}, \bibinfo{pages}{47--70}
(\bibinfo{year}{2000}).

\bibitem{doyle+2014}
\bibinfo{author}{Doyle, A.~P.}, \bibinfo{author}{Davies, G.~R.},
\bibinfo{author}{Smalley, B.}, \bibinfo{author}{Chaplin, W.~J.} \&
\bibinfo{author}{Elsworth, Y.}
\newblock \bibinfo{title}{Determining stellar macroturbulence using
	asteroseismic rotational velocities from {{Kepler}}}.
\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
\textbf{\bibinfo{volume}{444}}, \bibinfo{pages}{3592--3602}
(\bibinfo{year}{2014}).

\bibitem{tayar+2015}
\bibinfo{author}{Tayar, J.} \emph{et~al.}
\newblock \bibinfo{title}{Rapid {{Rotation}} of {{Low}}-mass {{Red Giants Using
			APOKASC}}: {{A Measure}} of {{Interaction Rates}} on the
	{{Post}}-main-sequence}.
\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
\textbf{\bibinfo{volume}{807}}, \bibinfo{pages}{82} (\bibinfo{year}{2015}).

\bibitem{schofield+2019}
\bibinfo{author}{Schofield, M.} \emph{et~al.}
\newblock \bibinfo{title}{The {{Asteroseismic Target List}} for {{Solar}}-like
	{{Oscillators Observed}} in 2 minute {{Cadence}} with the {{Transiting
			Exoplanet Survey Satellite}}}.
\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
\textbf{\bibinfo{volume}{241}}, \bibinfo{pages}{12} (\bibinfo{year}{2019}).

\bibitem{mathur+2019}
\bibinfo{author}{{Mathur}, S.} \emph{et~al.}
\newblock \bibinfo{title}{{Revisiting the impact of stellar magnetic activity
		on the detection of solar-like oscillations by Kepler}}.
\newblock \emph{\bibinfo{journal}{Frontiers in Astronomy and Space Sciences}}
\textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{46} (\bibinfo{year}{2019}).
\newblock \eprint{1907.01415}.

\bibitem{amard+matt2020}
\bibinfo{author}{{Amard}, L.} \& \bibinfo{author}{{Matt}, S.~P.}
\newblock \bibinfo{title}{{The Impact of Metallicity on the Evolution of the
		Rotation and Magnetic Activity of Sun-like Stars}}.
\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
\textbf{\bibinfo{volume}{889}}, \bibinfo{pages}{108} (\bibinfo{year}{2020}).
\newblock \eprint{2001.10404}.

\bibitem{fleming+2019}
\bibinfo{author}{Fleming, D.~P.}, \bibinfo{author}{Barnes, R.},
\bibinfo{author}{Davenport, J. R.~A.} \& \bibinfo{author}{Luger, R.}
\newblock \bibinfo{title}{Rotation {{Period Evolution}} in {{Low}}-mass
	{{Binary Stars}}: {{The Impact}} of {{Tidal Torques}} and {{Magnetic
			Braking}}}.
\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
\textbf{\bibinfo{volume}{881}}, \bibinfo{pages}{88} (\bibinfo{year}{2019}).

\bibitem{halbwachs1986}
\bibinfo{author}{{Halbwachs}, J.~L.}
\newblock \bibinfo{title}{{Common proper motion stars in the AGK 3.}}
\newblock \emph{\bibinfo{journal}{Astron. Astrophys.s}}
\textbf{\bibinfo{volume}{66}}, \bibinfo{pages}{131--148}
(\bibinfo{year}{1986}).

\bibitem{white+2013}
\bibinfo{author}{{White}, T.~R.} \emph{et~al.}
\newblock \bibinfo{title}{{Interferometric radii of bright Kepler stars with
		the CHARA Array: {\ensuremath{\theta}} Cygni and 16 Cygni A and B}}.
\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
\textbf{\bibinfo{volume}{433}}, \bibinfo{pages}{1262--1270}
(\bibinfo{year}{2013}).
\newblock \eprint{1305.1934}.

\bibitem{maxted+2015}
\bibinfo{author}{Maxted, P. F.~L.}, \bibinfo{author}{Serenelli, A.~M.} \&
\bibinfo{author}{Southworth, J.}
\newblock \bibinfo{title}{Comparison of gyrochronological and isochronal age
	estimates for transiting exoplanet host stars}.
\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
\textbf{\bibinfo{volume}{577}}, \bibinfo{pages}{A90} (\bibinfo{year}{2015}).

\bibitem{gallet+delorme2019}
\bibinfo{author}{{Gallet}, F.} \& \bibinfo{author}{{Delorme}, P.}
\newblock \bibinfo{title}{{Star-planet tidal interaction and the limits of
		gyrochronology}}.
\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
\textbf{\bibinfo{volume}{626}}, \bibinfo{pages}{A120} (\bibinfo{year}{2019}).
\newblock \eprint{1905.06070}.

\bibitem{benbakoura+2019}
\bibinfo{author}{Benbakoura, M.}, \bibinfo{author}{R{\'e}ville, V.},
\bibinfo{author}{Brun, A.~S.}, \bibinfo{author}{{Le Poncin-Lafitte}, C.} \&
\bibinfo{author}{Mathis, S.}
\newblock \bibinfo{title}{Evolution of star-planet systems under magnetic
	braking and tidal interaction}.
\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
\textbf{\bibinfo{volume}{621}}, \bibinfo{pages}{A124} (\bibinfo{year}{2019}).

\bibitem{ceillier+2016}
\bibinfo{author}{Ceillier, T.} \emph{et~al.}
\newblock \bibinfo{title}{Rotation periods and seismic ages of {{KOIs}} -
	comparison with stars without detected planets from {{Kepler}} observations}.
\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
\textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{119--125}
(\bibinfo{year}{2016}).

\end{thebibliography}

\input{tabulate.tex}

%\end{document}
